### 2017-06-05 sheets/talk-6/sheet-6.tex
Partial solutions for 6: Coequalizer of sets

>>>>

\begin{answer}
  \begin{itemize}
    \item[(a)]
      \begin{itemize}
        \item[(i)]
          \begin{proof}
            To show that $S$ is symmetric and reflexive, we choose $n := 0$. $R_0$ is by construction symmetric and reflexive.
            We will show symmetrie and reflexivity of $S_n$ seperately.
            \begin{itemize}
              \item[\emph{Reflexivity:}]
                Let $x \in X$. We show $\forall n\in\nat: (x, x) \in R_n$ by induction on $n\in\nat$.
                \begin{itemize}
                  \item[$n=0$:]
                    $R_0$ is by construction reflexive.
                  \item[$n \rightarrow n+1$:]
                    We know $(x, x) \in R_n$ by the inductive hypositive and show $(x, x) \in R_{n+1}$. By applying the definition of $R_{n+1}$
                    it is enough tow show $(x, x) \in R_n \land (x, x) \in R_n$ that is true with the inductive hypositive.
                \end{itemize}
                \item[\emph{Symmetrie:}]
                We show $\forall n\in\nat: \forall x_1,x_2 \in X: (x_1, x_2) \in R \Rightarrow (x_2, x_1) \in R$ by induction on $n\in\nat$.
                \begin{itemize}
                  \item[$n=0$:]
                    $R_0$ is by construction symmetric.
                  \item[$n \rightarrow n+1$:]
                    We know $\forall x_1,x_2 \in X: (x_1, x_2) \in R_{n} \Rightarrow (x_2, x_1) \in R$ by the inductive hypositive and have to show
                    $\forall x_1, x_2 \in X: (x_1, x_2) \in R_{n+1} \Rightarrow (x_2, x_1) \in R_{n+1}$.
                    Let $x_1, x_2 \in X$ with $(x_1, x_2) \in R_{n+1}$. By unfolding the definition of $R_{n+1}$ we get a $x$ with
                    $(x_1, x) \in R_n \land (x, x_2) \in R_n$ and have to show $(x_2, x_1) \in R_{n+1}$.
                    We apply the definition of $R_{n+1}$ and show $(x_2, y) \in R_n \land (x, x_1) \in R_n$.
                    Applying the inductive hypositive we it is enough to show $(x, x_2) \in R_n \land (x_1, y) \in R_n$ that is true by assumption. \qedhere
                \end{itemize}
            \end{itemize}
          \end{proof} % (a) (i)

        \item[(ii)]
          \begin{proof}
            To show that $S$ contains $R$ we choose $n := 0$. $R_0$ contains $R$ by construction. \\
            We show $\forall n\in\nat: \forall x_1,x_2\in X: (x_1, x_2) \in R \Rightarrow (x_1, x_2) \in R_n$ by induction on $n\in\nat$.
            \begin{itemize}
              \item[$n=0$:]
                $R_0$ contains $R$ by construction.
              \item[$n \rightarrow n+1$:]
                We assume $\forall x_1, x_2 : X, (x_1, x_2) \in R \Rightarrow (x_1, x_2) \in R_n$ by the induction hypositive.
                Let $x_1, x_2 \in X$ and $(x_1, x_2) \in R$. We show $(x_1, x_2) \in R_{n+1}$.
                We apply the definition of $R_{n+1}$ and show $(x_1, x_1) \in R_n \land (x_1, x_2) \in R_n$.
                The first we know with (a)(i) and the second by assumption. \qedhere
            \end{itemize}
          \end{proof} % (a) (ii)

        \item[(iii)]
          \begin{proof}
            Let $m,n\in\nat$ and $x_1, x_2 \in X$. We show $n \le m \Rightarrow (x_1, x_2) \in R_n \Rightarrow (x_1, x_2) \in R_m$ by induction on $n\in\nat$.
            \begin{itemize}
              \item[$n=0$:]
                We have $n \le 0$ and thus $n = 0$ and $(x_1, x_2) \in R_0$. We have to show $(x_1, x_2) \in R_0$ that is true by assumption.
              \item[$n \rightarrow n+1$:]
                We know $n \le m+1$ and $(x_1, x_2) \in R_n$. By the induction hypositive we also know
                $n \le m \Rightarrow (x_1, x_2) \in R_n \Rightarrow (x_1, x_2) \in R_m$.
                We have to show $(x_1, x_2) \in R_{m+1}$. We have two cases:
                \begin{itemize}
                  \item[$n = m+1$:]
                    The goal follows with the assumption $(x_1, x_2) \in R_{n=m+1}$.
                  \item[$n \le m$:]
                    We show $(x_1, x_2) \in R_{m+1}$ by applying the definition of $R_{m+1}$ and have to show $(x_1, x_1) \in R_m \land (x_1, x_2) \in R_m$.
                    The first we know with (a)(i) and the second by assumption. \qedhere
                \end{itemize}
            \end{itemize}
          \end{proof} % (a) (iii)

        \item[(iv)]
          \begin{proof}
          % TODO
          \end{proof} % (a) (iv)

        \item[(v)]
          \begin{proof}
          % TODO
          \end{proof} % (a) (iv)

      \end{itemize}

      % TODO Do we need part (a) at all?
    \item[(b)]
      \begin{itemize}
        \item[(i)]
          \begin{proof}
            Let $x \in X$. We have $i(s(x)=[s(x)]$ and $i(t(x))=[t(x)]$. It remains to show that $[s(x)]=[t(x)]$. Therefore it is enough to show that $s(x) \sim t(x)$.
            This is true since $\sim$ contains $R$ and $(s(x), t(x)) \in R$ by the construction of $R$.
          \end{proof} % (b) (i)

        \item[(ii)]
          \begin{proof}
            Let $(y_1, y_2) \in \sim$. Then be definition of $\sim$ we have a $n\in\nat$ such that $(y_1, y_2) \in R_n$.
            We show $\forall n\in\nat: \forall y_1,y_2 \in Y: (y_1, y_2) \in R_n \Rightarrow f (y_1) = f (y_2)$ by induction on $n\in\nat$.
            \begin{itemize}
              \item[$n=0$:]
                We have $(y_1, y_2) \in R_0$. This means $(y_1, y_2) \in R \lor (y_2, y_1) \in R \lor y_1 = y_2)$.
                We have to show $f(y_1) = f(y_2)$. Case analysis.
                \begin{itemize}
                  \item[1.] $(y_1,y_2) \in R$. Then we have $y_1 = s(a) \land y_2 = t(t)$ for some $a \in X$. $f (s (a)) = f (t (a))$ holds since $f$ commutes.
                  \item[2.] $(y_1,y_2) \in R$. Then we have $y_2 = s(a) \land y_1 = t(t)$ for some $a \in X$. $f (t (a)) = f (s (a))$ holds since $f$ commutes.
                  \item[3.] $y_1=y_2$. Then we have $f(y_1) = f(y_2)$.
                \end{itemize}
              \item[$n \rightarrow n+1$:]
                We have $(y_1, y_2) \in R_{n+1}$. Therefore we have a $y$ such that $(y_1, y) \in R_n \land (y, y_2) \in R_n$.
                With the inductive hypositive we know $\forall y_1, y_2 \in Y: (y_1, y_2) \in R_n \Rightarrow f (y_1) = f (y_2)$.
                By instanciating the inductive hypositive we know $f (y_1) = f (y) \land f (y) = f (y_2)$.
                Thus we get $f (y_1) = f (y_2)$ \qedhere
            \end{itemize}
          \end{proof} % (b) (ii)

        \item[(iii)]
          \newcommand{\choice}[1]{\set{#1}}
          We have to assume the axiom of choice. Because every equivalence class is non-empty, we get a function
          $\choice{ \_ } \from Y/\sim \to Y$ such that $\choice{ e } \sim x$ for every equivalence class $e$ and every object $x \in e$.

          We now define $\bar{f}(e) := f (\choice e)$.

          We have to show that the diagramm commutes. Note that commutativity of this diagramm is equivalent to $\bar{f} \of i =f$.
          Let $y \in Y$. We have to show $\bar{f}(\choice{i (y)}) = f(y)$. With (ii) it is enough to show $\choice{i (y)} \sim y$.
          This holds since $\choice{i (y)} = \choice{[y]} \sim y$, since $y \sim y$. \qedhere

          We finally have to show that $\bar{f}$ is the only function with that property.
          Let $\tilde{f} \from C \to A$ with $\tilde{f} \of i = f$. Let $c \in Y /\sim$.
          Then $\bar{f}(c) = f(\choice{c}) = \tilde{f}(i(\choice{c}) = \tilde{f}([\choice{c}]) = \tilde{f}(c)$.

        \item[(iv)]We know that there is only \emph{one} coequalizer (up-to isomorphism). By definition we have shown that our construction is \emph{a} coequalizer.
      \end{itemize}

  \end{itemize}
\end{answer}
